Multiple Kernelized Correlation Filters based High Speed Target Following

### 2017-04-07 draft.tex
MKCF Part Finished - Algorithm Added

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}

% Include other packages here, before hyperref.

@@

\newcommand{\matt}[1]{ \color{red} Matt: #1  \color{black}}
\newcommand{\aneesh}[1]{ \color{blue} Aneesh: #1  \color{black}}
\newcommand{\burak}[1]{ \color{green} Burak: #1  \color{black}}
\newcommand{\emmett}[1]{\color{violet} Emmett: #1  \color{black}}
\begin{document}

@@

\section{Multiple Kernelized Correlation Filter Based Tracking}
\label{sc:MKCF}
The KCF with Multi-channel features outperforms the other state-of-the-art object traking algorithms both in terms of run-time performance and tracking accuracy. However, it lack scale adaptation module or the naive scale adaptation method added into the KCF reduces the frames per second from $\geq300$ fps to less than $100$ fps. One straightforward method is to run detection on ROIs with different sizes determined by pre-defined scale ratios \cite{henriques2015high,tang2015multi,ma2015long,bibi2015multi,li2014scale}. All these method increases the computational complexity of tracking by running detection on a number of ROIs. Another scale update method in Correlation Filter framework was proposed by \cite{zhang2014fast}. It uses the MOSSE tracker to estimate translation of an object. The scale is updated in a naive way where the confidence map is used to determine the scale change between successive frames. For instance, their method assumes similar scale in between two consecutive frames given similar confidences. With this simple method, we do not need to run detection on different ROIs at a given frame and perform tracking at $\geq300$ fps. In this study, we propose the use of Multiple KCFs in an intuitive way to perform robust scale-adaptive tracking at more than $300$ fps. Our approach is inspired by \cite{ma2015long} where two KCFs are employed as translation and scale filters. It first estimates translation using the translation filter learned on \textit{target}$+$\textit{background} area. Then, the scale filter learned on the \textit{target} area is used to estimate new scale of the target at the estimated position. Application of translation and scale filter at each frame reduces run-time performance ($\leq50 fps$) as we need to run detection and training on both filters. Similarly, we learn three different correlation filters specializing on different aspects of tracking and addresses the weakness of each other, resulting in more robust tracking. We name these filters as \textit{target}+\textit{small background} translation filter ($R_{t}^{S}$), \textit{target-only} scale filter ($R_{s}$) and \textit{target}+\textit{large background} translation filter ($R_{t}^{L}$). Unlike \cite{ma2015long}, by running a single filter at each frame, we can achieve the targeted operation frame rate.
\begin{figure}[!t]
\includegraphics[width=0.5\textwidth]{figures/Filters_Details.pdf}
\caption{The three filters called as medium ROI translation filter, target ROI scale filter and large ROI translation filter are shown. Also, the hanning window and desired Gaussian response for each filter are displayed.}
\label{fig:Filters}
\end{figure}

>>>>

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{algorithm}% http://ctan.org/pkg/algorithms
\usepackage{algpseudocode}% http://ctan.org/pkg/algorithmicx% Include other packages here, before hyperref.

@@

\newcommand{\matt}[1]{ \color{red} Matt: #1  \color{black}}
\newcommand{\aneesh}[1]{ \color{blue} Aneesh: #1  \color{black}}
\newcommand{\burak}[1]{ \color{green} Burak: #1  \color{black}}
\newcommand{\emmett}[1]{\color{violet} Emmett: #1  \color{black}}
\usepackage{forloop}
\newcounter{ct}
\newcommand{\markdent}[1]{\forloop{ct}{0}{\value{ct} < #1}{\hspace{\algorithmicindent}}}
\newcommand{\markcomment}[1]{\Statex\markdent{#1}}
\begin{document}

@@

\section{Multiple Kernelized Correlation Filter Based Tracking}
\label{sc:MKCF}
The KCF with Multi-channel features outperforms the other state-of-the-art object traking algorithms both in terms of run-time performance and tracking accuracy. However, it lack scale adaptation module or the naive scale adaptation method added into the KCF reduces the frames per second from $\geq300$ fps to less than $100$ fps. One straightforward method is to run detection on ROIs with different sizes determined by pre-defined scale ratios \cite{henriques2015high,tang2015multi,ma2015long,bibi2015multi,li2014scale}. All these method increases the computational complexity of tracking by running detection on a number of ROIs. Another scale update method in Correlation Filter framework was proposed by \cite{zhang2014fast}. It uses the MOSSE tracker to estimate translation of an object. The scale is updated in a naive way where the confidence map is used to determine the scale change between successive frames. For instance, their method assumes similar scale in between two consecutive frames given similar confidences. With this simple method, we do not need to run detection on different ROIs at a given frame and perform tracking at $\geq300$ fps. In this study, we propose the use of Multiple KCFs in an intuitive way to perform robust scale-adaptive tracking at more than $300$ fps. Our approach is inspired by \cite{ma2015long} where two KCFs are employed as translation and scale filters. It first estimates translation using the translation filter learned on \textit{target}$+$\textit{background} area. Then, the scale filter learned on the \textit{target} area is used to estimate new scale of the target at the estimated position. Application of translation and scale filter at each frame reduces run-time performance ($\leq50 fps$) as we need to run detection and training on both filters. Similarly, we learn three different correlation filters specializing on different aspects of tracking and addresses the weakness of each other, resulting in more robust tracking. We name these filters as \textit{target}+\textit{small background} translation filter ($R_{t}^{S}$), \textit{target-only} scale filter ($R_{s}$) and \textit{target}+\textit{large background} translation filter ($R_{t}^{L}$). Unlike \cite{ma2015long}, by running a single filter at each frame, we can achieve the targeted operation frame rate. The fig.~\ref{fig:Filters} shows the size of the ROIs associated with $R_{t}^{S}$, $R_{t}^{L}$, and $R_{s}$ in addition to the hanning windows assigned and desired Gaussian responses assigned to each one.

\begin{figure}[!t]
\includegraphics[width=0.5\textwidth]{figures/Filters_Details.pdf}
\caption{The three filters called as medium ROI translation filter, target ROI scale filter and large ROI translation filter are shown. Also, the hanning window and desired Gaussian response for each filter are displayed.}
\label{fig:Filters}
\end{figure}

Our MKCF based tracking framework employs different capabilities and tasks to each correlation filter learned temporally. In \cite{ma2015long, danelljan2014accurate}, a scale filter is learned on \textit{target-only} area whereas \cite{henriques2015high, li2014scale, bibi2015multi, tang2015multi} uses a correlation filter learned on \textit{target+background} area to find the optimal scale in scale space. To learn the scale filter, $R_{s}$, we follow a similar approach to \cite{ma2015long}. We believe that translation filter needs to include background information to better discriminate target from background, however, the goal of the scale filter is to estimate the right size of the target, not to discriminate it from background. Also, by using a smaller ROI we can reduce the size of the template to learn the scale filter, resulting in higher speed scale estimation module. Finally, the scale filter help us on the track re-initialization module which includes running an object proposals algorithm to boxes bounding the objects in the scene. By using the scale filter in re-initialization module, we can reduce the element-wise operations compared to the translation filters. The \textit{target+small background} area translation filter, $R_{t}^{S}$, is assigned a larger template size than $R_{s}$ and smaller than $R_{t}^{L}$. It is employed to estimate translation and scale similar to \cite{henriques2015high}. Finally, the \textit{target+large background} area translation filter, $R_{t}^{L}$ , estimates only the translation of a target.

\begin{algorithm}
	\caption{The MKCF Tracking Algorithm.}\label{alg:MKCF}
	\begin{algorithmic}[1]
	\State \textbf{Input} : Initial bounding box $x_{0}$, frame counter $fc$, scale filter frequency $n$,
	\State \textbf{Output} : 
								\If{$fc\:\%\:n=0$} \Comment{Condition 1}
										\State Estimated Target State $x_{t} = (x_{t-1},y_{t-1},s_{t})$,
										Scale filter (\textit{target-only}) model $R_{s}$.
								     \EndIf
								     \If{$fc\:\%\:n=1$}\Comment{Condition 2}
										\State Estimated Target State $x_{t} = (x_{t},y_{t},s_{t_1})$,
										Large Area Translation Filter model $R_{t}^{L}$.
								     \EndIf
								     \If{$fc\:\%\:n>1$}\Comment{Condition 3}
										\State Estimated Target State $x_{t} = (x_{t},y_{t},s_{t})$,
										Small Area Translation Filter model $R_{t}^{S}$.
								     \EndIf
	\Procedure{track}{$x_{t-1},y_{t-1},s_{t-1}$} 
								 \State // Translation Estimation
								 \State Transit Particle Filter to the frame $t$ and compute the mean of prior pdf $x_{t} = (x_{t},y_{t},s_{t-1})$;
								 \State // Translation Estimation
								 \State Crop the ROI for the $R_{t}^{L}$, or $R_{t}^{S}$ given $x_{t}$
								 and estimate translation ($x_{t}$,$y_{t}$) using $R_{t}^{L}$ (Condition 2) or $R_{t}^{S}$ (Condition 3),
								 \State Skip translation estimation for $R_{s}$ (Condition 1);
								 \State // Scale Estimation
								 \State Crop the ROI for the $R_{s}$ and estimate scale, $s_{t}$, using $R_{s}$ (Condition 1) or $R_{t}^{S}$ (Condition 2), 
								 \State Skip it for $R_{t}^{L}$ (Condition 1),
								 \State Scale pool for $R_{s}$ : $\lbrace1.05,1.0,1/1.05\rbrace$, and for $R_{t}^{S}$ : $\lbrace1.02,1.0,1/1.02\rbrace$;
								 \State // Update Translation
								 \State Perform Importance Re-sampling for Particle Filter and compute the mean of posterior pdf $x_{t} = (x_{t},y_{t},s_{t})$;
								 \State // Model Update
								 \If{$max(y_{R_{s}}) \geq T_{R_{s}}$}
								 	\State Update $R_{s}$ (Condition 1);
								 \EndIf							 
								 \If{$max(y_{R_{t}^{L}}) \geq T_{R_{t}^{L}}$} 
								 	\State Update $R_{t}^{L}$ (Condition 2);
								 \EndIf	
								 \If{$max(y_{R_{t}^{S}}) \geq T_{R_{t}^{S}}$}
								 	\State Update $R_{t}^{S}$ (Condition 3);
								 \EndIf		
	\EndProcedure	
	\end{algorithmic}
\end{algorithm}
